Epigraphic Echoes in Epigrams

### 2016-02-09 panels/EAGLE_2016_submission_47.tex

\section{Panelists}
\begin{description}
\item[Marion Lamé]\emph{Centre Camille Jullian, MMSH, CNRS, France Email: mlame@mmsh.univ-aix.fr} Collaborates with the Laboratorio di Cultura Digitale of the University of Pisa. She has worked and works on several digital epigraphic projects (IGLouvre, TSS, Memorata Poetis...) and collaborates to collective dissemination of digital practices (EpiDoc). Her researches are dedicated to Digital Epigraphy applied especially to complex epigraphical situation and device (multilingualism, multialphabetism...).

@@

@@

\item[Pr. Enrica Salvatori] \emph{University of Pisa
Email: enrica.salvatori@unipi.it} Specialized in Medieval history and Director of the Laboratorio di Cultura Digitale of the University of Pisa. She works in the digitization process of inscriptions of Pisa, included epigrams, and in projects of public history concering the valorization of epigraphs.
[http://pisaeislam.humnet.unipi.it/ - http://epigrapisa.humnet.unipi.it/]

\item[Dr. Eleonora Santin] \emph{CNRS - Laboratoire HiSoMA (UMR 5189) Email: eleonora.santin@mom.fr} Specialized in Greek Epigraphy and Greek Philology., she is a CNRS researcher with a personal program entitled Musa Epigraphica: new approaches for the study and the edition of the Greek epigraphic poetry and works on the digitization of epigraphic epigrams.

\end{description}
\end{document}

>>>>

\section{Panelists}
\begin{description}
\item[Dr. Marion Lam\'e]\emph{Centre Camille Jullian, MMSH, CNRS, France Email: mlame@mmsh.univ-aix.fr} Collaborates with the Laboratorio di Cultura Digitale of the University of Pisa. She has worked and works on several digital epigraphic projects (IGLouvre, TSS, Memorata Poetis...) and collaborates to collective dissemination of digital practices (EpiDoc). Her researches are dedicated to Digital Epigraphy applied especially to complex epigraphical situation and device (multilingualism, multialphabetism...).

@@

\item[Dr. Mia Trentin] \emph{University of Venice Email: trentin.mia@unive.it} Mia Trentin is specialized in Medieval Epigraphy and Latin Palaeography, focusing on medieval ways of communication and expression through the analysis of historical graffiti writing. She collaborates with prof. Flavia De Rubeis for the project Memorata Poetis.

@@

\item[Pr. Enrica Salvatori] \emph{University of Pisa
Email: enrica.salvatori@unipi.it} Specialized in Medieval history and Director of the Laboratorio di Cultura Digitale of the University of Pisa. She works in the digitization process of inscriptions of Pisa, included epigrams, and in projects of public history concering the valorization of epigraphs.
[\url{http://pisaeislam.humnet.unipi.it/} - \url{http://epigrapisa.humnet.unipi.it/}]

\end{description}

\section*{Acknowldgements}
Eleorona Santin for her suggestions while preparing this panel.

\end{document}
